T-reX: A python package to quantify waste and material footprints in current and future LCA databases

### 2024-03-06 latex_files/main.tex
V2 almost

\end{frontmatter}
\cbox{Total word count: ~6000, Limit: 5000 (can be easily condensed)}

%% main text
\section{Introduction}
\label{sec:introduction}
\cbox{Section word count: 1450}
\cbox{To be split into two (sub) sections: Introduction and Background, can be easily condensed by 200 words or so.}
\input{introduction.tex}

>>>>

\end{frontmatter}
\cbox{Total word count: ~5000, Limit: 5000}

% list of abbreviations
\begin{table}[H]
    \centering
    \caption{List of abbreviations}
    \label{tab:abbreviations}
    \begin{tabular}{ll}
    \toprule
    CML & Centrum voor Milieuwetenschappen (Centre for Environmental Science) \\
    CRM & Critical Raw Material \\
    CSI & Crustal Scarcity Indicator \\
    CSP & Crustal Scarcity Potential \\
    EDIP & Environmental Design of Industrial Products \\
    EOL & End-of-Life \\
    FOEN & Swiss Federal Office for the Environment \\
    IAM & Integrated Assessment Model \\
    LCA & Life Cycle Assessment \\
    LCIA & Life Cycle Impact Assessment \\
    LFP & Lithium Iron Phosphate \\
    LiMn$_2$O$_4$ & Lithium Manganese Oxide \\
    NCA & Nickel Cobalt Aluminum \\
    NMC & Nickel Manganese Cobalt \\
    PWF & Product Waste Footprint \\
    RCP & Representative Concentration Pathway \\
    ReCiPe & A standard LCIA method set \\
    SSPs & Shared Socioeconomic Pathways \\
    UBP & Umweltbelastungspünkte (Environmental Impact Points) \\
    \bottomrule
    \end{tabular}
    \end{table}

%% main text
\section{Introduction}
\label{sec:introduction}
\cbox{Section word count: 1500}
\cbox{To be split into two (sub) sections: Introduction and Background, can be easily condensed by 200 words or so.}
\input{introduction.tex}
